---
title: "Web Data Collection First Assignment"
author: "Carolina Matamoros"
output:
  html_document: default
  pdf_document: default
---


```{r setup, include=FALSE}
source("../packages.r")
```


<br>

##### 1. NYC flights

Use the "nycflights13" package to answer the following questions!

a. How many variables and observations does the data.frame "flights" from the nycflights13 package contain?
b. Select the flights that started from NYC at the first day of each month!
c. Sort flights by time of arrival!
d. How many flights started from all the NYC airports in 2013?
e. Which carrier had the biggest mean net delay (departure delay minus arrival delay), which the lowest?
f. Inspect visually how the net delays are distributed!

```{r}
library(nycflights13)
# To answer a
str(flights)
dim(flights)
# answer: 336776 observadtions and 19 variables in the dataset

# To answer b a possibility is to create a subset that fullfils those requirements.
flights_1<- filter(flights, day == 1)
flights_1JFK<- filter(flights_1, origin == "JFK")
flights_1LGA<- filter(flights_1, origin == "LGA")
flights_NY <-bind_rows(flights_1JFK,flights_1LGA)
head(flights_NY)
str(flights_NY)
dim(flights_NY)

# To answer c is required to use a function that sorts the observations by time of arrival

flights_NY1 <- arrange(flights_NY, arr_time) # For the selected flights
flights_SORT <- arrange(flights, arr_time) # For the all the flights
head(flights_NY1)
head(flights_SORT)


# d is the same procedure but instead of filtering by day = 1 would be by year = 2013

flights_2013<- filter(flights, year == 2013)
flights_JFK13<- filter(flights_2013, origin == "JFK")
flights_LGA13<- filter(flights_2013, origin == "LGA")
flights_NY_2013<-bind_rows(flights_JFK13,flights_LGA13)
head(flights_NY_2013)
str(flights_NY_2013)
dim(flights_NY_2013)

# Therefore there were 215941 flights that started from NYC during 2013.

# e) THis requires the creation of a new variable that measures delay followed by its main descriptive statistics by carrier

flights_delay <- mutate(flights, delay = dep_delay - arr_delay)

flights_delay_bycarrier <- group_by(flights_delay, carrier)
class(flights_delay_bycarrier)

summarize(flights_delay_bycarrier, n_deps = n())
summarize(flights_delay_bycarrier, mean_delay = mean(delay, na.rm = TRUE))

# Therefore the carrier with the largest mean delay time was AS with 15.8 and the smallest was by F9 with -1.72

# f inspect visually the delays... thorugh plots?

hist(flights_delay$delay)

# simple bar chart
plot(as.factor(flights_delay$delay))

```

<span style="color:blue">
Add comment like this! (just copy the <span>...</span> lines for future comments in the Rmd file.)
</span>


<br>

##### 2. Baby names

Use the "babynames" package to answer the following questions!

a. Which time period does the data frame cover?
b. What has been the most frequent name in the US since 1880? (hint: you might need the group_by() as well as the sum() function)
c. Use graphical means to determine since which year the name "Kim" became more popular as a female than a male name! (hint: grouping by two variables is helpful here! For the plot, use "year" on the x axis and "total count" on the y axis! Furthermore, this Stackoverflow post helps you understand how to plot two lines in one chart: https://stackoverflow.com/questions/2564258/plot-two-graphs-in-same-plot-in-r)

```{r}
# a) Time period of the data frame

library(babynames)
str(babynames)
summary(babynames)

# answer The data frame goes from 1880 to 2015

# b) The names that were used the most since 1880?

resumen <-babynames %>% group_by(name) %>% summarise(totalm = sum(n, na.rm = TRUE))

resumen <-arrange(resumen,desc(totalm))
head(resumen)

# answer b) James is the most used name since 1880 with 5144205 uses.

# C) for Kim when did Kim for Male  became less popular than for Female

kim1880_2015<- filter(babynames, name == "Kim")

resumenKim <-kim1880_2015 %>% group_by(sex, year) %>% summarise(totalm2 = sum(n, na.rm = TRUE))

resumenKim <-arrange(resumenKim, year)

library(ggplot2)
kimdraw <- ggplot(data=resumenKim,aes(x=year,y=totalm2,linetype=sex)) +
  geom_line(mapping=aes(color=sex)) +
  labs(title="Kim babies by gender and year") +
  scale_x_continuous(breaks=seq(1880,2015,25)) 
kimdraw


# answer C Therefore the tendency of which gender has more Kims changes right before 1955 

```


