---
title: "Assignment 3_Carolina Matamoros_167311"
author: "Carolina Matamoros"
date: "20 de febrero de 2018"
output:
  html_document: default
  pdf_document: default
---

### 0. Preparation: Load packages

```{r load packages, include=FALSE}

library(stringr)
p_needed <- c("rvest", # scraping suite
              "httr", "httpuv", # suites to ease HTTP communication
              "RSelenium", # access Selenium API
              "pageviews", "aRxiv", "rtweet", "ROAuth", "gtrendsR", "ggmap", # access various web APIs
              "robotstxt", # parse robots.txt files
              "readr", # imports spreadsheet data
              "haven", # imports SPSS, Stata and SAS files
              "magrittr", #  for piping
              "plyr", # for consistent split-apply-combines
              "dplyr",  # provides data manipulating functions
              "stringr", # for string processing
              "lubridate", # work with dates
              "jsonlite", # parse JSON data
              "devtools", # developer tools
              "networkD3", # tools to process network data
              "ggplot2", # for graphics
              "tidyr", # for tidying data frames
              "broom", # for tidying model output
              "janitor", # for basic data tidying and examinations
              "reshape2", # reshape data 
              "xtable", # generate table output
              "stargazer", # generate nice model table
              "babynames", # US babynames dataset 
              "nycflights13" # data set on all 336776 flights departing from NYC in 2013
)
packages <- rownames(installed.packages())
p_to_install <- p_needed[!(p_needed %in% packages)]
if (length(p_to_install) > 0) {
  install.packages(p_to_install)
}
lapply(p_needed, require, character.only = TRUE)
```



### 1. The ultimate regular expression

Find a regular expression that matches any text!


```{r}
# your code here

# 
mystring <- "Pasito a pasito, suave suavecito \nNos vamos pegando poquito a poquito"
str_extract_all(mystring,".+") # in breaks by lines only
str_extract_all(mystring,".*") # in breaks by lines counting spaces
```


### 2. Finding strings that are matched by regular expressions

Describe the types of strings that conform to the following regular expressions and construct an example that is matched by the regular expression.

a. [0-9]+\\$


```{r}
# Example
str_extract_all("Phone 150$, TV 690$", "[0-9]+\\$") # Answer: describes prices in dollars

mystring <- "1203 .rgnargn 667 1203$"
str_extract_all(mystring,"[0-9]+\\$")

str_extract_all("Phone 150&, TV 690&", "[0-9]+\\&") 
# your code here
```
The first expression looks for and matches all the digit characters in the string that end with the dollar sign $, which can be useful when looking for prices. When the example was slightly changed and runned again it served to verify that the backslash were the ones providing the instruction or the ones working as "metacharacters". In the trial it looked for digists followed by the "& sign.

b. b[a-z]{1,4}


```{r}
# Example


mystring <- "bajo bello bueno bastión"
str_extract_all(mystring,"b[a-z]{1,4}")

# your code here
```
As it is it looks for the up to 4 alphabetical characters that are after a b. Nonetheless the code would be way more useful if it had the regex like "\\\\b[a-z]{1,4}\\\\b" since in that way it would look for short words of up to 4 characters in minor case.

c. .*?\\.txt$

```{r}

mystring <- "Pasito a pasito, suave suavecito \nNos vamos pegando poquito a poquito.txt"
str_extract_all(mystring,".*?\\.txt$")


```
This should be able to match strings chains that end in .txt, would be useful for lists of text files. Given that it looks for text ending in .txt in any break provided by (.*)


d. \\d{2}/\\d{2}/\\d{4}

```{r}
# Example
mystring <- "12323/35/8351iwuhth dhdgh/23893/24132/"
str_extract(mystring,"\\d{2}/\\d{2}/\\d{4}")


```
This one is useful to look for and match string chains cointaining 2 digits followed by 2 digits that are followed for 4 digits more. Each groups is saparated by a slash, this means it is useful to look for dates dd/mm/yyyy or mm/dd/yyyy (USA style).

e. <(.+?)>.+?</\\1>

```{r}
# Example
mystring <- c("18/07/1984","1","Two","<tan>.</tan>","<a>whateever I want will show</a>"," <crazytag>This is an HTML element</crazytag>")
str_extract(mystring,"<(.+?)>.+?</\\1>")


```
This set is usefull for extracting strings surrounded by "openning and closing tags", in other words strings surrounded by <tag> and </tag>. These is particularly useful to extract text form HTML since the elements are surrounded by these particular set of characters. Nonetheless it can only do it once by every string element.


### 3. Manipulating an email address

Consider the mail address  datalover89[at]aol[dot]com. Now, complete the following tasks.

a. Transform the string to a standard mail format (i.e., replace the square brackets with the appropriate symbols) using regular expressions.
b. Now extract the local-part ("datalover89") and the domain ("aol") separately. 

```{r}
email <- "datalover89[at]aol[dot]com"
# a) 
email <- "datalover89[at]aol[dot]com"
email <- sub(pattern = "\\[at\\]", replacement = "@", x = email)
email <- sub(pattern = "\\[dot\\]", replacement = "\\.", x = email)
email

# b)
unlist(str_extract_all(email, ".+(?=@)|[[:alpha:]].+(?=\\.)"))


```


### 4. A secret message
The following code hides a secret message. Crack it with R and regular expressions. Once you have cracked it, try to collapse the solution in one single string. <i>Hint: Some of the characters are more revealing than others!</i>

```{r}
secret <- "clcopCow1zmstc0d87wnkig7OvdicpNuggvhryn92Gjuwczi8hqrfpRxs5Aj5dwpn0TanwoUwisdij7Lj8kpf03AT5Idr3coc0bt7yczjatOaootj55t3Nj3ne6c4Sfek.r1w1YwwojigOd6vrfUrbz2.2bkAnbhzgv4R9i05zEcrop.wAgnb.RqoE65fGEa1otfb7wXm24k.6t3sH9zqe5fy89n6Ed5t9kc4fR905gmc4Ogxo5nhk!gr"
unlist(str_extract_all(secret, "[:upper:]|[:punct:]"))
```



### 5. Inspecting Trump's tweets

The following code gives you access to a dataset of Donald Trump tweets that he posted over the course of the 2016 election campaign. Focus on the `Tweet_Text` variable and come up with your own shot at this data. Requirement: Use at least 3 different regular expressions and 3 different functions from the `stringr` package for your analysis!

```{r, warning = FALSE, message = FALSE}
library(readr)
trump_df <- read_csv("https://raw.githubusercontent.com/Currie32/Tweet-Like-Trump/master/tweets.csv")

#To verify that detect works. looking for tweets with tags aka @
trump_df2 <- trump_df[,3]
str_detect(trump_df2$Tweet_Text[1:10], "(?<=@).+")
head(trump_df2)

#Now to play with it creating subsets of the original dataset
head(filter(trump_df2, str_detect(trump_df2[["Tweet_Text"]], "(?<=@).+")))
taggedtweet<- filter(trump_df2, str_detect(trump_df2[["Tweet_Text"]], "(?<=@).+"))

taggedHillary<- filter(taggedtweet, str_detect(taggedtweet[["Tweet_Text"]], "(?<=@)HillaryClinton"))

taggedSons<- filter(taggedtweet,str_detect(taggedtweet[["Tweet_Text"]],"(?<=@)EricTrump|(?<=@)DonaldJTrumpJr|(?<=@)IvankaTrump"))

 taggedHimself<- filter(taggedtweet, str_detect(taggedtweet[["Tweet_Text"]], "(?<=@)realDonaldTrump"))

totaltweets <- nrow(trump_df)
taggs <- nrow(taggedtweet)
TagHillary <- nrow(taggedHillary)
TagSons <- nrow(taggedSons)
TagHimself <- nrow(taggedHimself)

taggs/totaltweets
TagHimself/totaltweets
TagHimself/taggs
TagHillary/totaltweets

HCmentions <- nrow (na.omit(str_match(trump_df2$Tweet_Text, "[Hh][Ii][a-zA-Z]{1,}[Rr][Yy][Cc][Ll][a-zA-Z]{1,}[Oo][Nn]|[Hh][Ii][a-zA-Z]{1,}[Rr][Yy] [Cc][Ll][a-zA-Z]{1,}[Oo][Nn]" )))

HCmentions
TagHillary

TagHillary/HCmentions
1/(TagHillary/HCmentions)

wordlength <-str_count(unlist(str_extract_all(trump_df2$Tweet_Text,"\\w+")))

summary(wordlength)
sd(wordlength)

hist(wordlength, 
     main="Trump's words", 
     xlab="Word Length", 
     border="black", 
     col="purple",
     xlim=c(1,15),
     breaks=50)

```

As conclusions from the data used. It was interesting to see that over 50% of the sample were tweets tagging other twitter uses, out of those around 40% (38.14) are tagging himself, or about 20% of the entire sample. It surprised me that less than 1% tagged Hillary Clinton, is very likely that the she is mentioned directly without a tag. 

This was latter verified, she was mentioned by her fullname 281 times, 4.39 times more than when she was directly tagged. 

Overall the word usage was pretty simple keeping it in general bellow 4 characters, the 2 and 3 character words are heavily used. The mean and meadian are both heavily affected by the 30 character outlier, in any case this shows the simple word vocabulary used for twitter by then candidate Trump.